A free/open-source Kazakh-Tatar machine translation system

### 2013-04-13 paper/paper.tex
need Ilnar's help
adding affiliation

\author{Ilnar Salimzyanov\\
  Affiliation / Address line 1\\
  Affiliation / Address line 2\\
  Affiliation / Address line 3\\
  \email{email@domain}  \And
  Jonathan North Washington\\
  Departments of Linguistics\\
  and Central Eurasian Studies\\
  Indiana University\\
  Bloomington, Indiana 47405 USA\\
  \email{jonwashi@indiana.edu}  \And
  Francis Morton Tyers\\
  Departament de Llenguatges\\
  i Sistemes Informàtics\\
  Universitat d'Alacant\\
  E-03877 Alacant\\
  \email{ftyers@dlsi.ua.es}}

@@

\subsection{Morphotactic differences}
2 or 3 specific examples
\subsection{Lexical and morphological differences}
2 or 3 specific examples
\subsection{Syntactic differences}
%2 or 3 specific examples
There are a number of syntactic differences in Tatar and Kazakh, which include differences in verb valencies in equivalent translations, FIXME, and FIXME.

>>>>

\author{Ilnar Salimzyanov\\
  Kazan Federal University\\
  Kazan, Republic of Tatarstan\\
  Russian Federation\\
  \email{ilnar.salimzyan@gmail.com}  \And
  Jonathan North Washington\\
  Departments of Linguistics\\
  and Central Eurasian Studies\\
  Indiana University\\
  Bloomington, Indiana 47405 USA\\
  \email{jonwashi@indiana.edu}  \And
  Francis Morton Tyers\\
  Departament de Llenguatges\\
  i Sistemes Informàtics\\
  Universitat d'Alacant\\
  E-03877 Alacant\\
  \email{ftyers@dlsi.ua.es}}

@@

\subsection{Morphotactic differences}
2 or 3 specific examples
%FIXME: Ilnar, I can't think of anything for this...

\subsection{Lexical and morphological differences}
2 or 3 specific examples
> present progressive
%FIXME: Ilnar, could you come up with some good examples of this?
> ... ?

\subsection{Syntactic differences}
%2 or 3 specific examples
There are a number of syntactic differences in Tatar and Kazakh, which include differences in verb valencies in equivalent translations, FIXME, and FIXME.
